---
title: 'EDS 221 Day 5 Tasks and Activities: Tilapia'
author: "Halina Do-Linh"
date: "8/13/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(here)
library(janitor)
library(skimr)
```

Read in the data as us_tilapia_imports

```{r}
tilapia_df <- read_csv(here("data", "us_tilapia_imports.csv"))

View(tilapia_df)

summary(tilapia_df)
names(tilapia_df)
dim(tilapia_df)
# skim(tilapia_df)

# read.csv gave me a slightly different data set then read_csv where the years had an X in front of i.e. X1995 and there were no NA's just blanks
```

Use pivot_longer() to reshape the data into long format (currently, the variable “year” is spread across multiple columns). Remember to store the output so you will be able to use the reshaped data this creates.

```{r}

tilapia_df_long <- tilapia_df %>% 
  pivot_longer(-country, names_to = "year", values_to = "volume")

```

Check the class of the year column. What is it, and why do you think that’s the case? Then, coerce the year column to numeric (e.g. using mutate() and as.numeric() in combination)

```{r}
tilapia_df_long$year <- as.numeric(tilapia_df_long$year)
```

Use dplyr::group_by() %>% summarize() to find the total US tilapia imports by year, store as yearly_tilapia_tot

```{r}
yearly_tilapia_tot <- tilapia_df_long %>% 
  group_by(year) %>% 
  summarize(volume = sum(volume, na.rm = TRUE))

```

Create a ggplot line graph of total US tilapia imports for all years in yearly_tilapia_tot. Update axis labels (include units as necessary), then export your graph as a .png to figs.

```{r}
yearly_tilapia_plot <- ggplot(data = yearly_tilapia_tot, aes(x = year, y = volume)) +
  geom_line() +
  labs(x = "Year", y = "Country")

ggsave(here("figs", "yearly_tilapia_plot.png"))

```
Create a subset that only retains imports from Ecuador, Honduras, Costa Rica, and Mexico (you decide what to name this)

```{r}

tilapia_subset <- yearly_tilapia_tot %>% 
  filter(country %in% c("Ecuador", "Honduras", "Costa Rica", "Mexico"))

# %in% the in operator asks in the country columns does this or this OR this exist?

```

Create a ggplot graph of total US tilapia imports over time, for those four countries in the subset you created above, separated by country. Update axis labels, add a title, customize your color scheme, update the theme. Export a .jpg of your graph to figs.

```{r}
yearly_tilapia <- tilapia_df_long %>% 
  filter(country %in% c("Ecuador", "Honduras", "Costa Rica", "Mexico")) %>% 
  group_by(country, year) %>%
  summarize(volume = sum(volume, na.rm = TRUE)) 
  

ggplot(data = yearly_tilapia, aes(x = year, y = volume)) +
  geom_point(aes(color = country)) +
  geom_line(aes(color = country)) +
  labs(x = "Year", y = "Volume (thousands of pounds)", title = "Total US Imports of Tilapia") +
  theme_light()
```

